Actuator line modeling of vertical-axis turbines

### 2018-05-03 paper.tex
Uncomment pdfoutput for arXiv
Set as preprint
Add 2017 Boudreau article; resolves #39

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

Reynolds-averaged Navier--Stokes (RANS) turbulence models computed on 3-D
body-fitted (blade-resolved) grids can do a good job predicting the mean
performance and near-wake structure of a VAT, though their effectiveness depends
on the turbulence model
applied~\cite{Bachant2016-BR-CFD,Lam2016,Alaimo2015,Boudreau2015,Marsh2015}.
However, 3-D blade-resolved RANS presents a huge computational expense---on the
order of 1,000 CPU hours per simulated second with contemporary hardware---since
it must resolve fine details of the blade boundary layers, which will preclude
its use for array analysis until the availability of computing power increases
sufficiently. It is therefore necessary to explore simpler models that can
predict the turbine loading and flow field with acceptable fidelity, but that
are economical enough to not require high performance computing, at least for
individual devices.

>>>>

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
\pdfoutput=1

@@

Reynolds-averaged Navier--Stokes (RANS) turbulence models computed on 3-D
body-fitted (blade-resolved) grids can do a good job predicting the mean
performance and near-wake structure of a VAT, though their effectiveness depends
on the turbulence model
applied~\cite{Bachant2016-BR-CFD,Lam2016,Alaimo2015,Boudreau2017,Marsh2015}.
However, 3-D blade-resolved RANS presents a huge computational expense---on the
order of 1,000 CPU hours per simulated second with contemporary hardware---since
it must resolve fine details of the blade boundary layers, which will preclude
its use for array analysis until the availability of computing power increases
sufficiently. It is therefore necessary to explore simpler models that can
predict the turbine loading and flow field with acceptable fidelity, but that
are economical enough to not require high performance computing, at least for
individual devices.
